### 2015-04-13 implementation.tex
rework gaps.
Minor updates, start of implementation section.

\section{Implementation}
\label{sec:implementation}

\todo{.5 page overview}

@@

@@

\subsection{Abstract \& Concrete Specs}
	\todo{1 page}

>>>>

%\begin{figure}
%\includegraphics[width=\columnwidth]{figs/spack-find-output.pdf}
%\end{figure}

\section{The Spack Package Manager}
\label{sec:implementation}

We have developed {\it Spack}, the Supercomputing PACKage manager, based on our
software needs Lawrence Livermore National Laboratory.
Spack solves the software matrix problem by allowing {\it parametric} builds.
Each package in Spack is parameterized by its name, version, architecture, compiler, 
compiler version, build options, and by its dependencies.
Like other systems, Spack allows multiple build variants to be installed at once,
but it provides novel, recursive {\it spec} syntax.  Specs are concise
expressions for partially constrained software dependence graphs. The same
spec syntax can be used on the command line to request new build 
configurations, or to query installed packages over many dimensions.

Spack borrows ideas from Nix to support multiple installations with 
cryptographic hashes, but it goes further and provides a build environment
that takes many burdens off of the package writer.  In particular, Spack uses
compiler wrappers to automatically add {\tt RPATHs} for {\it all} dependencies
to installed binaries, so that package authors do not have to.  Compiler
wrappers also give the packager more control over the build: package authors
can more easily port to new platforms by filtering compiler flags.

@@

%\begin{figure}
%\begin{grammar}
%  <spec-list> ::= \{ <spec> [ <dep-list> ] \}
%  
%  <dep-list>  ::= \{ `\textsf \textasciicircum' <spec> \}
%
%  <spec>      ::= <id> [ options ]
%  
%  <options>   ::= \{ `@' version-list | `+' <variant> \newline
%                  | `-' <variant> ~~~| `~' <variant> \newline
%                  | `\%' <compiler> ~| `=' <architecture> \}
%                  
%  <variant>      ::= <id>
%
%  <architecture> ::= <id>
%
%  <compiler>     ::= <id> [ <version-list> ]
%
%  <version-list> ::= <version> [ \{ `,' version \} ]
%
%  <version>      ::= <id> | <id> `:' | `:' <id> | <id> `:' <id>
%
%  <id>           ::= [A-Za-z0-9_][A-Za-z0-9_.-]*  
%
%\end{grammar}
%\end{figure}

@@

\subsection{Abstract \& Concrete Specs}
	\todo{.75 page}
